Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-27 revisionMemo/rev1.tex
R1 done CD

		TO DO in paper: Strategies like those employed by Aronow et al do not directly model all relevant dependencies in the data \footnote{As Aronow et al explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.} but instead adjust the variance estimator.  While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will cause us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.
		Aronow et al. also explicitly note that their approach does not deal with issues of third order dependence.
		Aronow et al. approach does not deal with bias in parameter estimates.

@@

@@

		We have edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes we observe. We have also clarified the goals of the paper in the earlier sections.
		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance. 
		\item For part (a), we have clarified that our study does not address causal identification. We instead focuses on providing unbiased estimates of covariates, which improves inference for observational data.
		\item As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions...relates to SM's to-do below.
		\item Finally, we understand these goals are not always central political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Muchlinski et al. 2016; Colaresi and Mahmood 2017; Mueller and Rauh 2018. 

>>>>

		\item  \emph{
		We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator.\footnote{As Aronow et al. explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.}   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will cause us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.
		}
		%\item \textcolor{blue}{ \emph{
		%Aronow et al. also explicitly note that their approach does not deal with issues of third order dependence.
		%}}
		%\item \textcolor{blue}{ \emph{
		%Aronow et al. approach does not deal with bias in parameter estimates.
		%}}

@@

		\item {\emph{

@@

		\item  \emph{
For part (a), we have clarified that our study does not address causal identification. We instead focus on providing unbiased estimates of covariates, which improves inference for observational data. We have also edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes that we observe. We have also clarified the goals of the paper in the earlier sections.}
		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions...relates to SM's to-do below.}}
		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; Mueller and Rauh 2018. CD: Do I add this to text somewhere or leave as memo only?}
		}
